Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-07 doc/paper.tex
Computational section: started

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has a higher price. In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.  
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set. In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
     \subsection{Settings and the Parameters' choice}
     \fxnote{TODO: Marko}

	\subsection{Results on exact methods}
\fxnote{Marko: Solving of CP i MIP solvers are limited to 5 mins. }
	\section{Conclusions and Future Work}

>>>>

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has a higher price. In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.  
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set. In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
     \subsection{Settings and the choice of the Parameters}
      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB. The maximum computation time of each of our algorithms was set to 5 min.

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
      	\item Greedy + Shaking parameters:  $\mathrm{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\mathrm{OFFSET} = 0.3$,
        \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
	\subsection{Results and Discussion}

	\section{Conclusions and Future Work}
